`r glue::glue('Doublet benchmarking results: {params$dataset}')`

### 2024-07-15 analyses/cell-type-ewings/template_notebooks/auc-workflow/01-auc-results.Rmd

```{r}
# get a list of tumor cells based on those that have number of marker genes expressed 
# greater than the threshold 
tumor_cells <- markers_df |> 
  dplyr::mutate(gene_detected = dplyr:if_else(gene_expression > 0 , 1, 0)) |> 
  dplyr::group_by(barcodes) |> 
  dplyr::summarize(total_genes = sum(gene_detected)) |> 
  dplyr::filter(total_genes >= params$marker_threshold) |> 
  dplyr::pull(barcodes)

>>>>

```{r}
# get a list of tumor cells based on those that have number of marker genes expressed 
# greater than the threshold 
tumor_cells <- markers_df |> 
  dplyr::mutate(gene_detected = as.integer(gene_expression > 0)) |> 
  dplyr::group_by(barcodes) |> 
  dplyr::summarize(total_genes = sum(gene_detected)) |> 
  dplyr::filter(total_genes >= params$marker_threshold) |> 
  dplyr::pull(barcodes)

### 2024-07-15 analyses/doublet-detection/exploratory-notebooks/03_compare-benchmark-results.Rmd

      scdbl_tsv <- file.path(result_dir, glue::glue("{dataset}_scdblfinder.tsv"))
      scrub_tsv <- file.path(result_dir, glue::glue("{dataset}_scrublet.tsv"))
      sce_file <- file.path(data_dir, dataset, glue::glue("{dataset}_sce.rds"))

@@

For three out of four datasets, `scDblFinder` predicts a much larger number of doublets compared to other methods.

>>>>

      scdbl_tsv <- file.path(result_dir, glue::glue("{dataset}_scdblfinder.tsv"))
      scrub_tsv <- file.path(result_dir, glue::glue("{dataset}_scrublet.tsv"))
      sce_file <- file.path(data_dir, dataset, glue::glue("{dataset}.rds"))

@@

For two out of four datasets, `scDblFinder` predicts a much larger number of doublets compared to other methods.

### 2024-07-15 analyses/doublet-detection/template-notebooks/02_explore-benchmark-results.Rmd

# SCE, with ground truth included
sce_file <- file.path(
  data_dir, 
  glue::glue("{params$dataset}_sce.rds")
)

@@

  caret::confusionMatrix(
    # truth should be first
    table(
      "Truth" = doublet_df$ground_truth,
      "Prediction" = doublet_df[[pred_col]]
    ), 
    positive = "doublet"
  )

>>>>

# SCE, with ground truth included
sce_file <- file.path(
  data_dir, 
  glue::glue("{params$dataset}.rds")
)

@@

  caret::confusionMatrix(
    # truth should be first
    table(
      "Truth" = df$ground_truth,
      "Prediction" = df[[pred_col]]
    ), 
    positive = "doublet"
  )
